Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
update KD core idea

Expected implementation details ...

@@

\katja{Crazy idea: can we distill a reasoning path of a whole agent into a smaller model? I.e. instead of intelligent decision making that a large model performs for a complex task (search for X first, then look up Y, then formulate hypotheses Z) the student model learns the "protocols" of "customer support" and acts accordingly, without actually "understanding" why a particular action is good in a particular situation}

>>>>

@@

This way, the student model learns the "protocols" of how to solve different problems, as well as the essence of the relevant knowledge selected by the teacher LLM. 
%\katja{Crazy idea: can we distill a reasoning path of a whole agent into a smaller model? I.e. instead of intelligent decision making that a large model performs for a complex task (search for X first, then look up Y, then formulate hypotheses Z) the student model learns the "protocols" of "customer support" and acts accordingly, without actually "understanding" why a particular action is good in a particular situation}
